\documentclass[]{article}
\usepackage{graphicx}

\parindent=0pt
\usepackage[margin=0.5in]{geometry}

\begin{document}
\pagestyle{empty}
{\large\textbf{Research Notes}}
\begin{itemize}
    \item[*] Created on Oct 5, 2014
    \item[*] Modified on \today
    \item[*] Author info: Boyou Zhou\\
             8 St Mary's St, PHO 340, Boston, MA 02215\\
             Email: bobzhou@bu.edu, Phone: 617-678-8480
\end{itemize}


\rule[-0.1cm]{7.5in}{0.01cm}\\
\\
\noindent \textbf{Oct 5,2014}
\textit{PUFatt: Embedded Platform Attestation Based on Novel Processor-Based PUFs}
\indent		\begin{itemize}
            \item \textit{Attestation} Built-in technology against malicious codes.

            \item \textit{Prover and Verifier} Platform to be evaluated and another platform
            to demonstrate that prover is in a known and trustworthy state.

            \item \textit{PUF} Physically Unclonable Functions

            \item \textit{Challenge and response} To each given input, there is a unique hard-
            ware specific output.

            \item \textit{CRP} Chaellenge and Response Pairs

            \item \textit{Arbiter} Two inputs gate. If one signal is faster then the other, output
            is one, vice versa.

            \item \textit{Main idea} The idea is to use process variation to create a signauture
            as the difference between to identical circuits.  The info is stored with obfuscation 
            network inside memory. The CRP for security check is verified by machine learn scheme
            based on the pre-stored info.

            \item \textit{critics} In the side channel attack, the author did not specificly explain
            what kind of side channel attack he is talking about. I believe that side channel attack
            can be acheived by bypassing the obsfucation part.
        \end{itemize}

\noindent \textbf{Oct 6,2014}
\textit{Trends and Challenges of Emerging Physical-Disorder based Security}
\indent		\begin{itemize}
            \item \textit{von Neumann trick} Even if the coin flipping is not a even probability 
            event, by applying von Neumann trick, the game's probability can still be evenly 
            distributed.

            \item \textit{movtivation} Providing a variety of survey of recent related PUF-related
            developments and emphasizes on several promising future of PUF.

            \item \textit{main idea} Most of the PUFs have been designed with process variation and
            the way people to prove the idea of PUF is by using the arbiter to detect two identical
            circuits output timing difference.

            \item \textit{critics} Nothing real.

            \end{itemize}

\noindent \textbf{Oct 8,2014}
\textit{ClockPUF: Physical Unclonable Functions based on Clock Networks}
\indent		\begin{itemize}
                \item \textit{motivation} The hardware security is based on the Intellectual Property
                theft. Standard identification methods, like printed serial numbers, can be forged.
                One way to use PUF is to either leverage the bistable circuits elements, or are based
                on variations on the gate delays or leakage currents.

                \item \textit{Main Idea} This paper introduces ClockPUF. A methodology for tracking the 
                pairwise differences between sink latencies. A return path is required to determine which
                path is enabled.

                \item \textit{CRP} Use the tunable delay buffers to enhance the entropy of CLockPUFs and
                enable a challenge-response protocol.
            \end{itemize}

\noindent \textbf{Oct 9,2014}
\textit{Robust and Reverse-Engineering Resilient PUF Authentication and Key-Exchange by Substring Matching}
\indent		\begin{itemize}

                \item \textit{PAKE} Password-Authenticated Key Exchange

                \item \textit{motivation} A third party observer can also model the CRPs through a 
                communication model.

                \item \textit{main work} The author proposed a key-exchange protocol for substring matching. 
                The method is light-weighted and attack-resilient. The entire CRP combination will not be
                exposed to any prover. The start substring of the CRP provide for the verifier is randomly 
                chosen.

                \item \textit{POK} Physically Obfuscated Key Generator weak PUFs.

                \item \textit{PUF}  Strong PUFs need to implement a TRNG, a true random number generator.

            \end{itemize}

\noindent \textbf{Oct 10,2014}
\textit{High-Sensitivity Hardware Trojan Detection Using Multimodal Characterization}
\indent		\begin{itemize}

                \item \textit{main motivation} This paper is based on thermal and power characterization 
                techniques. 

                \item \textit{main argument} The author adds 20\% to 40\% of the process variation. The result
                shows that it is possible to detect trojans with 3-4 orders of magnitude smaller power consumptions 
                than the total power. \textbf{It is not the area of the IC chip. It is the power consumption.}
                
                \item \textit{thermal analysis} This analysis is based on the infrared image form the backside of 
                the chip. This work estimates the power mapping accurately. Generic research on the thermal analysis
                which may not be able to detect small changes for the infrared wavelength is too long to have a 
                high resolution.
       		\end{itemize}
\end{document}

