\documentclass[]{article}
\usepackage{graphicx}
\usepackage{amsmath}

\parindent=0pt
\usepackage[margin=0.5in]{geometry}

\begin{document}
\pagestyle{empty}
{\large\textbf{Research Notes}}
\begin{itemize}
    \item[*] Created on Oct 27, 2014
    \item[*] Modified on \today
    \item[*] Author info: Boyou Zhou\\
             8 St Mary's St, PHO 340, Boston, MA 02215\\
             Email: bobzhou@bu.edu, Phone: 617-678-8480
\end{itemize}

\rule[-0.1cm]{7.5in}{0.01cm}\\
\\
\noindent \textbf{Oct 27,2014}
\textit{High-level Synthesis for Run-time Hardware Trojan Detection and
Recovery}
\indent		\begin{itemize}
            \item \textit{main motivation} The author does not like the idea
            with side channel analysis. The author propose the idea to detect
            the trojan and then recover the chip to the normal state. 
            \item \textit{IP core trojan insertion} Two funciton-equivalent
            using IP cores from different vendors carrying the same trojan is
            not very likely.  
            \item \textit{NC RC} Normal Computation and Re-Computation
            \item \textit{related work} NC and PC computation's inconsistancy
            will be viewed as the insertion of harware trojan.
            \item \textit{architecture asurance} It's like the Boeing747 using
            three architectures to ensure the accuracy of computation.
            \item \textit{ILP} The auther considers the cost problem as an
            optimization problem. Pretty awesome they convert binary problem to
            a linear optimization problem.
            \item \textit{critics} Cost paid for getting two identical IP
            cores.
            \item \textit{high-level synthesis} GAUT, a high level synthesis
            tool.
            \end{itemize}

\noindent \textbf{Oct 28,2014}
\textit{Provably Complete Hardware trojan Detection Using Test Point Insertion}
\indent		\begin{itemize}
            \item \textit{delay detection compared to current testing} Delay
            testing is better than the leakage tesing, because of 
                \begin{itemize}
                    \item Linear dependence of delays on process variation
                    \item limited number of components
                \end{itemize}
            \item \textit{main motivation} In order to improve the performance
            of delay analysis in trojan detection, the author introduce testing
            point for the circuit for seperate parallel paths and enables their
            delay measurement.  A SAT-based input vector selection for
            characterizing each single path.
            \item \textit{ATPG} Automatic test pattern generation
            \item \textit{algorithm} Find all the reconvergence path and insert
            D-flipflops in order to use the timing analysis.
            \item \textit{critics} They added to much input cap due to the
            added flipflop.
       		\end{itemize}

\noindent \textbf{Oct 28,2014}
\textit{EC535 lab note}
\indent		\begin{itemize}
                \item \textit{I2c position gumstix} \\
                nc nc power gnd
                nc gpio17 nc nc
       		\end{itemize}

\noindent \textbf{Oct 29,2014}
\textit{PageRank}
\indent		\begin{itemize}
                \item \textit{assumption} How important a website is depends on
                how many links point towards it. The more being pointed, the
                more important it is.
                \item \textit{example} There is a small universe of examples,
                A, B, C, and D. At first, all the PR value for these four are
                evenly distributed as $0.25$. If A, B, C point at D, then they
                dump all their value to D, as D is $0.75$. It one node is
                pointing at multiple nodes, then the possibility will be evenly
                distributed. As A points at B and C, then each dumped
                possibility will be $0.125$. However, one PR value is not only
                depends on the dumped possibility but also being affected by
                the dump factor.
                \begin{equation}
                    PR(p_{i}) = \frac{1-d}{N} + d\sum\limits_{(p_{j}) \in
                    M(p_{i})} \frac{PR(p_{j})}{L(p_{j})}
                \end{equation}
                \item \textit{critics} The \textit{farm links} will alter the
                importance of a group of websites. There must be more fraud
                website detections for those websites.
                \item \textit{development} Penguin and Panda
                    \begin{itemize}
                        \item \textit{Penguin} It is aiming at detection of
                        cross language affection upon the eigenvalue, the
                        dumping factor.
                        \item \textit{panda} It is proposed to get rid of the
                        low quality websites.
                        \item \textit{link farm detection} This is a trade
                        secret of the company.
                    \end{itemize}
            \end{itemize}

\noindent \textbf{Oct 30,2014}
\textit{On Application of One-class SVM to Reverse Engineering-Based Hardware
Trojan Detection}
\indent		\begin{itemize}

                \item \textit{SVM} Support Vector Machine
                \item \textit{main motivation}
            \end{itemize}
\end{document}

